% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yabin Ping}

\basicInfo{
  \email{yabping@gmail.com} \textperiodcentered\ 
  \phone{(+86) 159-6818-3014} \textperiodcentered\ 
  \linkedin[Yabin Ping]{https://cn.linkedin.com/in/ping-yabin-a3225068}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University}, Shanghai, China}{Sept. 2012 -- Apr. 2015}
\textit{Master student} Computer Science(CS).
\datedsubsection{\textbf{Hunan Agriculture University}, Hunan, China}{Sept. 2007 -- Jun. 2011}
\textit{B.S.} in Computer Science(CS).


\section{\faCogs\ Skill Set}
\begin{itemize}[parsep=0.5ex]
	\item Programming Languages: Python，Golang， C/C++.
	\item Skills: Data structure \& algorithms, Thrift RPC, RabbitMQ, Celery, Redis, MySQL, Postgresql, Zookeeper
	\item Classes: Operating System, Data Structure, Networking, Database Principle
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Rajax Network Technology} Shanghai, China}{May. 2015 -- Present}
\role{Distribution Platform}{Technical Leader}
In order to improve the quality of take-out service,  a related problem is how to improve the transportation of foods to customers efficiently. So we design this system, and my contributions are:
\begin{itemize}
  \item Analysis of business architecture, design application architecture and technical architecture; 
  \item Implemented the core module of the system, including but not limited to order service，courier service, micro-service management etc.
  \item Optimize some API to achieve  better efficiency in time or storage.
  \item Design schedule algorithm and LBS algorithms to improve last mile problems. 
\end{itemize}

\datedsubsection{\textbf{Microsoft} Shanghai, China}{Apr. 2014 -- Jul. 2014}
\role{Azure web portal}{SDE}
Developed a web portal based on .Net framework. The technical parts are:
\begin{itemize}
  \item Use signalR technology to enable real-time push functions from server to browser.
  \item Furthermore I analyzed the web portal’s security issues, like XSS, CSRF, SQL injection attacks.
\end{itemize}

\datedsubsection{\textbf{Intel}}{Jul. 2013 -- Mar. 2014}
\role{DPDK VirtIO}{SDE}
\begin{itemize}
  \item Investigated the communcation ways between host machine and virtual machine. 
  \item Developed an automation test framework using Python. 
  \item As my first job, I also had learnt much about how to work together in a business company, and how to develop a product.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


\section{\faHeartO\ Honors and Awards}
\datedline{Scholarship, Award on Shanghai Jiao Tong University}{ Sept. 2013}
\datedline{IEEE Globecom best paper candidate}{Dec. 2014}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/yabping
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
